Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems

### 2017-11-10 LaTeX/Turnover.tex
weak selection invasion almost compilied

\begin{subequations}
\begin{align}
a &= w_a^\female \phi + w_A^\female \psi \\
b &= w_{AA}^\female \phi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\female \psi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \phi + w_{aa}^\female \psi \left( w_{aa}^\male w_a^\male \psi \right)\\
%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
\end{align}
\end{subequations}

@@

\begin{equation}\label{eq:BeqWAspread}
2(w_{Aa}^\female-w_{aa}^\female)w_{AA}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
\end{equation}

@@

\begin{equation}\label{eq:BeqWaspread}
(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{AA}^\male) \phi \psi >0
\end{equation}

@@

Generally, haploid selection expands the scenarios under which neo-W alleles can spread. 
For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection, c.f., Figure \ref{fig:SexAntagTighter} and Figure \ref{fig:SexAntagTighterMaleDrive}. 
Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$), Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}. 
Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$, Figure \ref{fig:regionPloidAntag}.

>>>>

\begin{subequations}
\begin{align}
a &= w_a^\female \phi + w_A^\female \psi \\
b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
\end{align}
\end{subequations}

@@

\begin{equation}\label{eq:BeqWAspread}
2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
\end{equation}

@@

\begin{equation}\label{eq:BeqWaspread}
(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
\end{equation}

@@

\textcolor{blue}{is this specific in any way to tight linkage, $r\approx0$?}

Generally, haploid selection expands the scenarios under which neo-W alleles can spread. 
For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}). 
Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}). 
Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
